Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
polishing

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J 
benchmark~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches may improve fault localization up to $73.7\%$
(\avgImprov\ on average). To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.
% \Mar{do we have supporting data to say that
%   the improvement is bigger when we care the most? for the cases SFL
%   performs worse? if yes, can we show average for that?}

>>>>

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J
benchmark~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches improves fault localization up to $73.7\%$
(\avgImprov\ on average). To sum up, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.
% \Mar{do we have supporting data to say that
%   the improvement is bigger when we care the most? for the cases SFL
%   performs worse? if yes, can we show average for that?}
